DATA 621 Homework #4

### 2019-11-15 hw4/HW4.Rmd
More work on HW4

---
title: "DATA 621 Homework #4"
author: "Critical Thinking Group 3"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    toc_depth: 3
    code_folding: "hide"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
require(gridExtra)
library(Amelia)
library(kableExtra)
library(caret)
library(DMwR)
library(scales)
library(RColorBrewer)
library(ROCR)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

```{r}
set.seed(42)
train_index <- createDataPartition(df$TARGET_AMT, p = .7, list = FALSE, times = 1)
train <- df[train_index,]
test <- df[-train_index,]
```

There are `r sum(train$TARGET_FLAG)` out of `r nrow(train)` records in the training data set that have been in an accident.  We want to correct the imballance in the dataset by over sampling this group so our model will do a better job identifying this minority group.

@@

```{r}
# Evaluating the model
eval <- data.frame(actual = test$TARGET_FLAG, predicted = predict(traditional_cv,newdata=test,type="raw"), prob = 
predict(traditional_cv,newdata=test,type="prob"))

@@

### Misc

@@

>>>>

---
title: "DATA 621 Homework #4"
author: "Critical Thinking Group 3"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    toc_depth: 3
    code_folding: "hide"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
require(gridExtra)
library(Amelia)
library(kableExtra)
library(caret)
library(DMwR)
library(scales)
library(RColorBrewer)
library(ROCR)
library(corrplot)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

```{r}
set.seed(42)
# ADAM THIS BROKE YOUR MODEL
#train_index <- createDataPartition(df$TARGET_AMT, p = .7, list = FALSE, times = 1)
train_index <- createDataPartition(df$TARGET_FLAG, p = .7, list = FALSE, times = 1)
train <- df[train_index,]
test <- df[-train_index,]
```

There are `r nrow(train[train$TARGET_FLAG == 1,])` out of `r nrow(train)` records in the training data set that have been in an accident.  We want to correct the imballance in the dataset by over sampling this group so our model will do a better job identifying this minority group.

@@

```{r, eval=FALSE}
# Evaluating the model
eval <- data.frame(actual = test$TARGET_FLAG, predicted = predict(traditional_cv,newdata=test,type="raw"), prob = predict(traditional_cv,newdata=test,type="prob"))

@@

### Manual Model

@@

## Amount Model

To select build a model of how much the claim amount will be we need to subset the training data to only include those that have accidents.  There will be `r train %>% filter(TARGET_FLAG == 1) %>% nrow()` data points in this set.

```{r}
amt_train <- train %>%
  filter(TARGET_FLAG == 1) %>%
  select(-INDEX, -TARGET_FLAG)
amt_test <- test %>%
  filter(TARGET_FLAG == 1)
```

```{r}
M <- amt_train %>%
  purrr::keep(is.numeric) %>%
  #mutate(TARGET_AMT = log(TARGET_AMT)) %>%
  na.omit() %>%
  cor(.)
corrplot(M, type = "upper")
```

It looks like `BLUEBOOK` is the only numeric variable that correlates with the claim amount.  We will use it as the baseline and see if we can improve this models.

```{r}
amt_fit <- lm(TARGET_AMT ~ BLUEBOOK, amt_train)
summary(amt_fit)
```
